A Formal Treatment of Bidirectional Typing

### 2024-01-15 tex/ESOP24/S5-synthesis.tex
[ tex ] Fix minor issues

      For a mode derivation of $\erase{\Gamma} |- \tmOpts^{\dir{d}}$, we first claim:
      \begin{claim}\label{lem:args-induction}
        For an argument list $\biargs$ and any partial substitution $\rho$ from $\Xi$ to $\emptyset$
        \begin{enumerate}
          \item either there is a minimal extension $\ext{\rho}$ of $\rho$ such that 
            \begin{equation} \label{eq:claim}
              \dom(\ext{\rho}) \supseteq \synvar(\biargs)
              \;\text{and}\;
%              \text{the domain of $\ext{\rho}$ contains $\synvar(\biargs)$ and\/} \quad
              \Gamma, \vars{x}_\isTerm{i} : \simsub{\Delta_i}{\ext{\rho}} |- \isTerm{t_i} \colon \simsub{A_i}{\ext{\rho}}^{\dir{d_i}}
            \end{equation}
            for $i = 1, \ldots, n$
          \item or there is no extension $\sigma$ of $\rho$ such that \eqref{eq:claim} holds.
        \end{enumerate}
      \end{claim}

>>>>

      For a mode derivation of $\erase{\Gamma} |- \tmOpts^{\dir{d}}$, we first claim:
      \begin{claim}\label{lem:args-induction}
        For an argument list $\biargs$ and any partial substitution $\rho$ from $\Xi$ to $\emptyset$
        either
        \begin{enumerate}
          \item there is a minimal extension $\ext{\rho}$ of $\rho$ such that 
            \begin{equation} \label{eq:claim}
              \dom(\ext{\rho}) \supseteq \synvar(\biargs)
              \;\text{and}\;
%              \text{the domain of $\ext{\rho}$ contains $\synvar(\biargs)$ and\/} \quad
              \Gamma, \vars{x}_\isTerm{i} : \simsub{\Delta_i}{\ext{\rho}} |- \isTerm{t_i} \colon \simsub{A_i}{\ext{\rho}}^{\dir{d_i}}
            \end{equation}
            for $i = 1, \ldots, n$, or
          \item there is no extension $\sigma$ of $\rho$ such that \eqref{eq:claim} holds.
        \end{enumerate}
      \end{claim}

### 2024-01-15 tex/ESOP24/S8-future.tex
[ tex ] Fix minor issues

For the second group, theories developed in set theory can often be restated in type theory and thus manageable for formalisation in a type-theoretic proof assistant. 
Such examples include frameworks developed by \citet{Allais2021,Ahrens2022,Fiore2022} in \Agda, which are relatively correct to their meta-language, although their expressiveness is limited to simply typed theories.
Our work belongs to the second group, as we aim for a formalism in a type theory to minimise the gap between theory and implementation.

>>>>

For the second group, theories developed in set theory can often be restated in type theory and thus manageable for formalisation in a type-theoretic proof assistant. 
Such examples include frameworks developed by \citet{Ahrens2022} in \Coq and \citet{Allais2021,Fiore2022} in \Agda, which are relatively correct to their meta-language, although their expressiveness is limited to simply typed theories.
Our work belongs to the second group, as we aim for a formalism in a type theory to minimise the gap between theory and implementation.
